Running an open experiment: transparency and reproducibility in soil and ecosystem

### 2016-02-11 manuscript/cpcrw_manuscript.Rmd
WC and BD calculations and results text

---
title: Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils
author: "Ben Bond-Lamberty^1^, Peyton Smith^2^, Vanessa Bailey^2^"
output: html_document
---
^1^Joint Global Change Research Institute, DOE Pacific Northwest National Laboratory, College Park, MD USA; 
bondlamberty@pnnl.gov

@@

@@

* Soil WC changes over incubation (Figure 1)

>>>>

---
title: Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils
author: "Ben Bond-Lamberty^1^, A. Peyton Smith^2^, Vanessa Bailey^2^"
output: html_document
---
^1^Joint Global Change Research Institute, DOE Pacific Northwest National Laboratory, College Park, MD USA; 
bondlamberty@pnnl.gov

@@

# 'Pretty n' function to round a numeric value and print that # of digits
pn <- function(x, n) formatC(round(x, n), digits = n, format = 'f')

@@

* Core BD

```{r coredata, echo=FALSE}
bd <- with(coredata, SoilDryMass_g / CoreVolume_cm3)
schist <- with(coredata, NonsoilMassLarge_g / (NonsoilMassLarge_g + SoilDryMass_g)) * 100
sdm <- coredata$SoilDryMass_g
```

The `r nrow(coredata)` experimental cores had a bulk density of `r pn(mean(bd), 2)` ± `r pn(sd(bd), 2)` (mean ± sd) g cm^-3^. Large (>2 mm) particles, primarily schist, comprised `r round(mean(schist), 0)`% ± `r round(sd(schist), 0)`% of the cores' total mass. Soil (≤2 mm) dry mass was `r round(mean(sdm), 0)` ± `r round(sd(sdm), 0)` g.

* Soil WC changes over incubation

```{r wc, echo=FALSE}
# wc and wc_alltrt are computed by 5-analyze.R script
wcbegin <- subset(wc_alltrt, stage == "Beginning")
wcend <- subset(wc, stage == "End")
wcendmean <- wcend$mean
names(wcendmean) <- wcend$Treatment
wcendsd <- wcend$sd
names(wcendsd) <- wcend$Treatment
```

Gravimetric water content was `r pn(wcbegin$mean, 2)` ± `r pn(wcbegin$sd, 2)` (min `r pn(wcbegin$min, 2)`, max `r pn(wcbegin$max, 2)`) at the beginning of the incubation (**Figure 1**). "Field moisture" cores were on average unchanged (`r pn(wcendmean["Field moisture"], 2)` ± `r pn(wcendsd["Field moisture"], 2)`) at the end of the incubation, but both the drought treatments, which did not differ from each other in their effect on gravimetric water content, had declined to `r pn(wcendmean["Drought"], 2)` ±  `r pn(wcendsd["Drought"], 2)`.

### 2016-02-11 manuscript_openexperiment/Open_experiment.Rmd
WC and BD calculations and results text

---
title: 'Running an open experiment: transparency and reproducibility in soil and ecosystem
  science'
author: "Ben Bond-Lamberty^1^, Peyton Smith^2^, Vanessa Bailey^2^"
date: "February 2, 2016"
output: word_document
---
^1^Joint Global Change Research Institute, DOE Pacific Northwest National Laboratory, College Park, MD USA; 
bondlamberty@pnnl.gov

>>>>

---
title: 'Running an open experiment: transparency and reproducibility in soil and ecosystem
  science'
author: "Ben Bond-Lamberty^1^, A. Peyton Smith^2^, Vanessa Bailey^2^"
date: "February 2, 2016"
output: word_document
---
^1^Joint Global Change Research Institute, DOE Pacific Northwest National Laboratory, College Park, MD USA; 
bondlamberty@pnnl.gov
